---
title: "Lab 15"
author: "Max Ward"
date: "4/30/2019"
output: html_document
---

```{r,echo=FALSE,message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(dplyr)        
library(fivethirtyeight)

major <-college_recent_grads
```
####Which major has the highest median pay, and does the higher pay have any connection to whether or not you get a job related to your major?
```{r,echo=FALSE,message = FALSE, warning=FALSE}
final2 <- major%>%
  group_by(major_category)%>%
  select(major_category, median)
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
ggplot(data = final2)+
  geom_point(mapping = aes(x = median, y = major_category, color = major_category))
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
final <- major%>%
  group_by(major_category)
summarise(final, avPay = mean(median))
```
As you can see from the graph and the data table Engineering tends to have the highest median pay.
```{r,echo=FALSE,message = FALSE, warning=FALSE}
perm_cor <- function(perms = 999, x, y)
{
  zero_vector = numeric(999)
  for (i in c(1:perms))
  {
    mix_y= sample(y, length(y), replace=FALSE)
    corr = cor(x, mix_y)
    zero_vector[i] = (corr)
  }
  return(zero_vector)
}
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
Lab15 = perm_cor(perms=999,major$'median', major$'college_jobs')
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
swag2 = cor(major$'median', major$'college_jobs')
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
m3 <- as_tibble(Lab15)
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
q2 <- sum(m3 > swag2)
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
ggplot(data = m3)+
  geom_histogram(mapping = aes(x= Lab15))+
  geom_vline(xintercept = swag2, color = 'blue') +
  ggtitle('Test Between Median and College Jobs')
```
```{r,echo=FALSE,message = FALSE, warning=FALSE}
pval2 <- q2/1000
pval2
```
Conclution: The graph and the p-value (the above number) show that there is very little correlation betweeen the majors median pay and if you get a job related to your major. So you might as well go for the one with the highest pay because your chance of getting a job related to you major is the same. I used a correlation permution test to see if the median pay and major jobs were related. This will help answer the overall team question of which major is best. 

###Reflection on Lab 2

####Max
I would say that my goals have stayed pretty much the same but I would put more emphasis on the doing a job I enjoy over making money. This class has not changed that I think that is just more of a personal thing. I leanred how to code in r and I leanred how to work in groups a lot better and to contribute more when I do work in groups. I would tell myself to use my time in class better, but I would tell myself to keep using the resores that I have to my advantage like google and the book. 
